Run the model

### 2019-05-30 scripts/model/2_run_model.Rmd
Added scripts

```{r}
# Load libraries
library(startR)
library(magrittr)
library(here)
library(cowplot)
library(furrr)
library(tidyverse)

@@

params %>% 
  knitr::kable(col.names = c("Parameter", "Value", "Source"), format = "latex", escape = F) %>% 
  cat(file = here("docs", "tab", "parameters.tex"))
```

@@

```{r}
# Create an empty tibble to store the results in the process
Rvec <- seq(0, 1, 0.05)
thetavec <- seq(0, 1, 0.1)

@@

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
  )
```

@@

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR
  )
```

>>>>

```{r}
# Load libraries
suppressPackageStartupMessages({
  library(startR)
  library(magrittr)
  library(here)
  library(cowplot)
  library(furrr)
  library(tidyverse)
})

@@

params %>% 
  knitr::kable(col.names = c("Parameter", "Value", "Source"),
               format = "latex",
               escape = F) %>% 
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  cat(file = here("docs", "tab", "parameters.tex"))
```

@@

```{r}
# Create combinations of R and theta
Rvec <- seq(0, 1, 0.05)
thetavec <- seq(0, 1, 0.1)

@@

```{r}
DF_1_no_trading <- DF_results_no_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    cost = b_vdsrevenue - VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
    cost_all = VDSrevenue_all - b_vdsrevenue_all,
    rel_cost_all = cost_all / b_vdsrevenue_all
  )
```

@@

```{r}
DF_1_with_trading <- DF_results_with_trading %>%
  filter(Country == "KIR") %>%
  left_join(Benchmark_results, by = "Country") %>%
  mutate(
    vessel_days_sold = b_vessel_days - Vessel_Days,
    sales_revenue = vessel_days_sold * VDSprice,
    all_VDSrevenue = VDSrevenue + sales_revenue,
    cost = b_vdsrevenue - all_VDSrevenue,
    rel_cost = cost / b_vdsrevenue,
    cost_pna_not_kir = VDSrevenue_notKIR - b_vdsrevenue_notKIR - sales_revenue,
    rel_cost_pna_not_kir = cost_pna_not_kir / b_vdsrevenue_notKIR,
    cost_all = VDSrevenue_all - b_vdsrevenue_all,
    rel_cost_all = cost_all / b_vdsrevenue_all
  )
```
